Extracting The Power of Dependent Types

### 2021-09-27 paper.tex
Don't use noindentparagraph
I find it rather ugly
Add keywords & CSS concepts

%\renewcommand{\paragraph}[1]{\textbf{\textit{#1. }}}
\setlength{\intextsep}{0pt}
%\AgdaNoSpaceAroundCode{}
\renewcommand\paragraph{\noindentparagraph}

@@

  Our main insight is that it is possible to
  express all three steps in a single language that supports
  both dependent typ\-es and reflection. Essentially,
  this allows us to express a program, its formal properties, and
  a compiler for it hand-in-hand, offering a lot of flexibility to programmers.
  We demonstrate this three-step approach by embedding a subset of
  the PostScript language in Agda, and illustrating it with several short examples.
  Thus we use the power of reflection to bring the benefits of dependent types to languages
  that had to go without them so far.
\end{abstract}
\maketitle

>>>>

%\renewcommand{\paragraph}[1]{\textbf{\textit{#1. }}}
\setlength{\intextsep}{0pt}
%\AgdaNoSpaceAroundCode{}
%\renewcommand\paragraph{\noindentparagraph}

@@

  Our main insight is that it is possible to
  express all three steps in a single language that supports
  both dependent typ\-es and reflection. Essentially,
  this allows us to express a program, its formal properties, and
  a compiler for it hand-in-hand, offering a lot of flexibility to programmers.
  We demonstrate this three-step approach by embedding a subset of
  the PostScript language in Agda, and illustrating it with several short examples.
  Thus we use the power of reflection to bring the benefits of dependent types to languages
  that had to go without them so far.
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011041.10011047</concept_id>
<concept_desc>Software and its engineering~Source code generation</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011041.10011046</concept_id>
<concept_desc>Software and its engineering~Translator writing systems and compiler generators</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010992.10010998.10010999</concept_id>
<concept_desc>Software and its engineering~Software verification</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011050.10011017</concept_id>
<concept_desc>Software and its engineering~Domain specific languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Software and its engineering~Source code generation}
\ccsdesc[300]{Software and its engineering~Translator writing systems and compiler generators}
\ccsdesc[300]{Software and its engineering~Software verification}
\ccsdesc[300]{Software and its engineering~Domain specific languages}

\keywords{embedded languages, program extraction, program verification, dependent types, reflection, Agda}

\maketitle
